---
title: "585 HW2"
author: "Weixiao Li"
date: "`r Sys.Date()`"
output:
   pdf_document:
       latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 1
```{r}
smartsales <- read.csv("C:/Users/16932/Desktop/MA585/smartsales.csv")
holidaygifts <- read.csv("C:/Users/16932/Desktop/MA585/holidaygifts.csv")
randomtopics <- read.csv("C:/Users/16932/Desktop/MA585/randomtopics.csv")
```

```{r}
travel_expenditure <- read.csv("C:/Users/16932/Desktop/MA585/travel expenditure.csv")

```


```{r}
library(TSA)
```


```{r}
plot.ts(travel_expenditure, ylab="expenditure of travel",xlab="Month")
title("Google Search for Travel Expenses from 2014 to date")

```
This plot shows a time series with a clear trend component.It has a clear downward trend over the years, indicating the decreasing expenditure of travel. I think the reason for it is the decreasing travel cost.


```{r}
plot.ts(holidaygifts, ylab="holiday gifts",xlab="Day")
title("Daily Google Search for Holiday Gifts in the Last 50 Days")
```
The plot of "holiday gifts" shows a clear seasonal pattern, it upwards sharply in one day, indicating the increased demand for gift-giving during these times.

```{r}
plot.ts(randomtopics, ylab="Random topics",xlab="Day")
title("Daily Google Search for Random Topics in the Last 50 Days")
```
This plot shows a time series with no clear trend or seasonal pattern and is poorly described.

# Problem 2 
```{r}
BosClimateData <- read.csv("C:/Users/16932/Desktop/MA585/BosClimateData (1).csv")
BosData=subset(BosClimateData,BosClimateData$STATION_NAME=="BOSTON LOGAN INTERNATIONAL AIRPORT MA US")
```

```{r}
plot.ts(BosData[,c(4:7)])
```
For TPCP and TSNW, there is not obvious trend.
For MMNT and MMXT, there are periodic trend.

```{r}
length(subset(BosData$TSNW,BosData$TSNW>1))/length(BosData$TSNW)
length(subset(BosData$MMXT,BosData$MMXT>80))/length(BosData$MMXT)
```
There are 38.5% months had total snowfall greater than a foot.
There are 70.83% months mean maximum temperature exceeded 80F.

# Problem 3
```{r}
plot.ts(rnorm(100))
```
It looks like random.

```{r}
plot.ts(rt(n=100, df=4))
```
The data is skewed in one direction, it suggest that the data generating process may not be Gaussian.
