---
title: "585 Final project"
author: "Weixiao Li"
date: "`r Sys.Date()`"
output:
   pdf_document:
       latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
data <- read.csv("D:/585/MA585-Time-series/Final/data/Boston-data.csv")
library(tseries)
library(lubridate)
library(forecast)
```

#Dataset
```{r}
data$Period.End.Month <- as.POSIXct( data$Period.End.Month, format = "%Y/%m/%d")
data$Median.Sale.Price <- as.numeric(gsub("\\$|K", "", data$Median.Sale.Price ))
data$Median.Sale.Price <- data$Median.Sale.Price * 1000
data <- data[, -1]
data <- data[,-3:-17]
data <- data[,-3:-4]
```


#Result
```{r}
data$Period.End.Month <- as.Date(data$Period.End.Month)
myts <- ts(data$Median.Sale.Price, start=c(year(data$Period.End.Month[1]), 1), frequency = 12)

plot.ts(myts, main = "Boston Real Estate Sale Price", xlab = "Date", ylab = "US Dollars")
```

```{r}
z <- decompose(myts)
plot(z)
logts <- log(myts)
myts_new=diff((logts),lag=12)
plot(myts_new,main = " Log of Boston Real Estate Sale Price")
adf.test(myts_new)

```
#ARIMA
```{r}
par(mfrow=c(1,2))
acf(myts_new)
pacf(myts_new)
```

In order to forecast the future price of Boston single family residential. I apply ARIMA model. From the ACF and PACF plots we can see that ACF cut off after lag2 and then decaying to zero, while PACF cut off nearlag 1 decaying to zero. So for the initial model,I choose ARIMA(0,1,1).

```{r}
# Fit a range of ARIMA models
model1 <- arima(myts, order = c(0,1,1), seasonal = list(order = c(0,1,1), period = 12))
model2 <- arima(myts, order = c(0,1,1), seasonal = list(order = c(1,1,1), period = 12))
model3 <- arima(myts, order = c(0,1,1), seasonal = list(order = c(1,1,1), period = 12))
model4 <- arima(myts, order = c(0,1,2), seasonal = list(order = c(0,1,1), period = 12))
model5 <- arima(myts, order = c(1,1,2), seasonal = list(order = c(1,1,1), period = 12))

# Compare the models using the AIC and BIC values
models <- c("model1", "model2", "model3", "model4","model5")
aic_values <- sapply(models, function(model) AIC(get(model)))
bic_values <- sapply(models, function(model) BIC(get(model)))

# Print the AIC and BIC values for each model
data.frame(Model = models, AIC = aic_values, BIC = bic_values)

# Choose the model with the lowest AIC value
best_model <- get(models[which.min(aic_values)])

```
Since there are many fit models, I chose the five most likely models based on the ACF and PACF plots. Through the results we can see that fit 1:ARIMA (1,1,1) has the smallest AIC and BIC values, so I choose ARIMA (1,1,1) as my final model for the following forecast.

```{r}
model1 <- arima(myts, order = c(0,1,1), seasonal = list(order = c(0,1,1), period = 12))
Bosfcast=forecast(model1,h=12)
Bosfcast
plot(Bosfcast,main=" Boston House Price Forecasts")
```
```{r}
# QQplot
myresiduals <- residuals(model1)
qqnorm(myresiduals)
qqline(myresiduals)
#diagnostic plots
tsdiag(model1)
```

```{r}
# Holt-Winters Seasonal Forecast
fit=HoltWinters(myts,seasonal="multiplicative")
forecast(fit,h=12)
# Compare forcasts

```





#Appendix
```{r}
# Fit a range of ARIMA models
model1 <- arima(myts, order = c(0,1,1), seasonal = list(order = c(0,1,1), period = 12))
model2 <- arima(myts, order = c(0,1,1), seasonal = list(order = c(1,1,1), period = 12))
model3 <- arima(myts, order = c(0,1,1), seasonal = list(order = c(1,1,1), period = 12))
model4 <- arima(myts, order = c(0,1,2), seasonal = list(order = c(0,1,1), period = 12))
model5 <- arima(myts, order = c(1,1,2), seasonal = list(order = c(1,1,1), period = 12))

# Compare the models using the AIC and BIC values
models <- c("model1", "model2", "model3", "model4","model5")
aic_values <- sapply(models, function(model) AIC(get(model)))
bic_values <- sapply(models, function(model) BIC(get(model)))

# Print the AIC and BIC values for each model
data.frame(Model = models, AIC = aic_values, BIC = bic_values)

# Choose the model with the lowest AIC value
best_model <- get(models[which.min(aic_values)])
```


